Draft

### 2022-07-22 ms.tex
written and revised by k 1st round, now without abstract & summary; version 0722

\red{Introduction of previous studies on QLFs for high-$z$ populations. mention Yung's paper, Ricarte \& Natarajan paper, recent Finkelstein's paper?
Also, I remember one paper of our former postdoc, Kim.
Also, recent Raffaella's student's paper and "highly-empirical paper" you introduced.
Please add more (I might miss some relevant papers.)}
\blue{
High-z
}

@@

\vspace{2mm}
\subsection{Model dependence}\label{sec:modep}
\red{KI: It'd be good to discuss the dependence of our results on key parameters such as $\tlife$.
You repeat the MCMC fitting with a fixed value of $\tlife$? Saying like for a longer $\tlife$,
the fitting results would never be improved.}

As described in \S~\ref{sec:model}, we introduce the parameter $\tau$ as a typical timescale 
for individual duration of quasar accretion activities, i.e. in each cycle $\tlife$ 
we assign Eddington ratio $\lambda$ following the parameterized ERDF for all BHs.
The extraction of this timescale essentially modifys the ERDF in the whole BH growth history, 
because the multiple sampling of $\lambda$ reduces the possibility of a BH accreting on average with $\lambda \gtrsim \lambda_0$ 
than single sampling. 
However at any time during growth, the ERDF of the BH population remains the same as at $z\sim$ 6, 
therefore we ensure treating all cosmic time equally.

% tau极端小，则非常小的lambda，不能解释 （且delta func？ 有必要说或是放在后面讨论？）

Hereafter we demonstrate the role of $\tlife$ on shaping the BHMF evolution and the consequent QLF. 
In the left panel of Fig.~\ref{fig:tau}, the BHMF at $z=6$ is calculated from setting $\tlife=$ 10, 18, and 50 Myr, 
and keeping the other parameters as the best-fit values for the $\fseed=0.01$ case.
While $\tlife \approx$ 18 Myr is the best-fit value, resulting in the BHMF which nicely matches the results in \citetalias{2010AJ....140..546W}, 
the other two cases demonstrate the sensitivity of the $\tlife$ value in producing the bulk of massive BHs 
and the slope in the high mass tail. 
For $\tlife=$ 10 Myr, the number of Eddington ratio assignment cycles increases to $\sim$ 80 
from $\sim$ 40 with the best-fit $\tlife$ value. 
Thus the possibility of continuous high Eddington ratio accretion along the growth is lower, 
suppressing the growth of massive BHs at $M_\bullet \gtrsim 10^8~\Msun$. 
On the other hand, for $\tlife=$ 50 Myr, with $\sim$ 16 times of multiple Eddington ratio assignment,
on average high values of $\lambda\gtrsim \lambda_0$ is non-negligibly realized in the BHMF evolution. 
Therefore in the high mass end of BHMF at $z=$ 6, the BH population is significantly overproduced than the constraints from observation.

The QLF at $z=6$ is shown in the right panel of Fig.~\ref{fig:tau}. 
In the conversion from BHMF to QLF, the ERDF is the same for different $\tlife$ values, 
following the $P(\lambda)$ in Eq.~(\ref{eq:Pl}) with $\lambda_0=0.87$ and a=0.20. 
Thus the deviation from the observed QLF in \citetalias{2018ApJ...869..150M}  shows similar trends as in the BHMF. 
i.e., $\tlife$ values lower (higher) than the best-fit one leads to the under(over)-production of the luminous quasar population.
We notice that the best-fit value of $\tlife$ favors a moderate fraction of $t_{\rm S}$, 
which regulates the BH growth and reproduces the quasar observation together with the other best-fit parameters in their reasonable ranges.

@@

\section{Discussion}
\vspace{2mm}
\subsection{Individual BH growth}\label{sec:evol}

>>>>

\red{Introduction of previous studies on QLFs for high-$z$ populations. mention Yung's paper, Ricarte \& Natarajan paper, recent Finkelstein's paper?
Also, I remember one paper of our former postdoc, Kim.
Also, recent Raffaella's student's paper and "highly-empirical paper" you introduced.
Please add more (I might miss some relevant papers.)}
\blue{
% High-z
}

@@

\vspace{2mm}
\subsection{Model dependence}\label{sec:modep}
As described in \S~\ref{sec:model}, we introduce the parameter $\tau$ as a typical timescale
for individual durations of quasar accretion activity.
Specifically, we assign an Eddington ratio $\lambda$ following the ERDF for all BHs in each cycle
with a time duration of $\tau$.
Variable accretion episodes in every cycle essentially modify the effective ERDF in the whole BH growth history,
because multiple sampling of $\lambda$ reduces the possibility of a BH growing with $\lambda \gtrsim \lambda_0$
compared to that with a single sampling of $\lambda$.
%However at any time during growth, the ERDF of the BH population remains the same as at $z\sim$ 6,
%therefore we ensure treating all cosmic time equally.
In what follows, we demonstrate the role of $\tlife$ in shaping the BHMF evolution and the consequent QLF.
% tau极端小，则非常小的lambda，不能解释 （且delta func？ 有必要说或是放在后面讨论？）

In the left panel of Fig.~\ref{fig:tau}, we present the BHMF at $z=6$ for three different values of $\tlife=10$, $18$, and $50$ Myr,
but keeping the other parameters as the best-fit values ($\lambda_0=0.87$ and $\alpha=0.20$) for the case with $\fseed=0.01$.
We note that $\tlife \approx$ 18 Myr is the best-fit value reproducing the BHMF consistent with that of \citetalias{2010AJ....140..546W}.
%the other two cases demonstrate the sensitivity of the $\tlife$ value in producing the bulk of massive BHs
%and the slope in the high mass tail.
For $\tlife=10$ Myr, the frequency of Eddington ratio assignment increases twice until $z=6$.
%to $\sim$ 80 from $\sim$ 40 with the best-fit $\tlife$ value.
Therefore, continuous and efficient growth of BHs with $\lambda \gtrsim \lambda_0$ is less likely to occur,
%high Eddington ratio accretion along the growth is lower,
suppressing the formation of BHs heavier than $M_\bullet \simeq 10^8~\Msun$.
Moreover, if a high Eddington ratio is given with a certain but low probability, the BH mass hardly increases
within $\tlife=10$ Myr, which is $\simeq 20\%$ of the $e$-folding timescale.
On the other hand, for $\tlife=$ 50 Myr, there is a non-negligible probability that
% $\sim$ 16 times of Eddington ratio assignment,
more BHs experience high accretion rates with $\lambda\gtrsim \lambda_0$ through their assembly history.
%high values of $\lambda\gtrsim \lambda_0$ is non-negligibly realized in the BHMF evolution.
Therefore, the high mass end of the BHMF is further extended and those massive populations are substantially
overproduced compared to the observed abundance.
%in the high mass end of BHMF at $z=$ 6, the BH population is significantly overproduced than the constraints from observation.

The QLF at $z=6$ is shown in the right panel of Fig.~\ref{fig:tau}.
%In the conversion from BHMF to QLF, the ERDF is the same for different $\tlife$ values,
%following the $P(\lambda)$ in Eq.~(\ref{eq:Pl}) with $\lambda_0=0.87$ and $\alpha=0.20$.
Overall, the dependence of the QLF on the choice of $\tau$ shows the same trend as in the BHMF,
%the deviation from the observed QLF of \citetalias{2018ApJ...869..150M} shows similar trends as in the BHMF.
i.e., higher (lower) $\tlife$ values lead to under(over)-production of the luminous quasar population.
The best-fit value of $\tlife (\simeq 18$ Myr) favors a moderate fraction of $t_{\rm S}$.
This suggests the importance of regulated growth of BHs to reproduce the shape of the observed BHMF and QLF.
%reproduces the quasar observation together with the other best-fit parameters in their reasonable ranges.
In \S\ref{sec:evol}, we apply this episodic accretion model to individual growth pathways of high-$z$ quasars
and demonstrate that normal seeding mechanisms can explain the existence of massive BHs with low luminosity
observed at $z\simeq 6-7$.

@@

\section{Discussion}
\label{sec:discussion}
\vspace{2mm}
\subsection{Individual BH growth}\label{sec:evol}
